plotly charts for sensitivity iteractive explorer html

### 2025-04-11 report_additionalCharts.Rmd
updating monetary units to euro 2025

@@

plotData <- left_join(
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
    group_by(tgt2030) %>% 
    mutate(min = min(value),
           max = max(value)),
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
    mutate(price_2030 = USS2017_2_EURO2020*value) %>%
    select(scenario, price_2030),
  by = "scenario") %>%
  mutate(text = paste0("Target Achieved: ", tgtAchieved, " % reduction", "\n2030 price: ", round(price_2030,2), " €/t CO2", "\nScenario: ", scenario, "\nTarget 2030: ", tgt2030, "%", "\nEfficiency: ", efficiency, "\nBiomass Limit: ", bioLim, "\nSensititivy limit: ", lim))

@@

nonAchieved2030 <- left_join(
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
    group_by(tgt2030) %>% 
    mutate(min = min(value),
           max = max(value)),
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
    mutate(price_2030 = USS2017_2_EURO2020*value) %>%
    select(scenario, price_2030),
  by = "scenario") %>%
  filter(diff >= 0.5 | diff <= -0.5) %>%
  select(scenario, price_2030, tgt2030, tgtAchieved, diff) %>%
  arrange(desc(abs(diff)))

>>>>

  USS2017_2_EURO2025 <- 1.212 # 1 USD 2017 = 1.212 EURO 2020 (1 US$2017 = 1.30 * 0.932642 €2025 = 1.212 €2025)
  # exchange rate = average of February 28, March 31, April 11, 2025 (0.960138 +  0.925734 + 0.912056)/3 = 0.932642 https://www.ofx.com/en-au/forex-news/historical-exchange-rates/yearly-average-rates/
  # CPI -> 1 $2017 = 1.30$2025 -> https://www.in2013dollars.com/us/inflation/2017?amount=1

  currencyConversion <- USS2017_2_EURO2025

@@

plotData <- left_join(
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
    group_by(tgt2030) %>% 
    mutate(min = min(value),
           max = max(value)),
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
    mutate(price_2030 = currencyConversion*value) %>%
    select(scenario, price_2030),
  by = "scenario") %>%
  mutate(text = paste0("Target Achieved: ", tgtAchieved, " % reduction", "\n2030 price: ", round(price_2030,2), " €/t CO2", "\nScenario: ", scenario, "\nTarget 2030: ", tgt2030, "%", "\nEfficiency: ", efficiency, "\nBiomass Limit: ", bioLim, "\nSensititivy limit: ", lim))

@@

nonAchieved2030 <- left_join(
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
    group_by(tgt2030) %>% 
    mutate(min = min(value),
           max = max(value)),
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
    mutate(price_2030 = currencyConversion*value) %>%
    select(scenario, price_2030),
  by = "scenario") %>%
  filter(diff >= 0.5 | diff <= -0.5) %>%
  select(scenario, price_2030, tgt2030, tgtAchieved, diff) %>%
  arrange(desc(abs(diff)))

### 2025-04-11 report_paperCharts.Rmd
updating monetary units to euro 2025

plotData <- df_beforeFilter %>%
  filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
  mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
         value = USS2017_2_EURO2020*value)

@@

plotData <- df %>% 
  filter(region == "EU27", period >= 2020, period <= 2050, scenario  == mainScen, variable %in% unlist(vars)) %>% 
  mutate(variable = factor(variable, levels=vars),
   value = USS2017_2_EURO2020*value) #%>% 
 # arrange(factor(variable, levels = rev(vars)))

>>>>

plotData <- df_beforeFilter %>%
  filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
  mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
         value = currencyConversion*value)

@@

plotData <- df %>% 
  filter(region == "EU27", period >= 2020, period <= 2050, scenario  == mainScen, variable %in% unlist(vars)) %>% 
  mutate(variable = factor(variable, levels=vars),
   value = currencyConversion*value) #%>% 
 # arrange(factor(variable, levels = rev(vars)))

### 2025-04-11 report_plotlyCharts.Rmd
updating monetary units to euro 2025

  plotData <- df_beforeFilter %>%
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
           value = USS2017_2_EURO2020*value) %>%
    mutate(value = round(value,2))

>>>>

  plotData <- df_beforeFilter %>%
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable %in% vars) %>%
    mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"),
           value = currencyConversion*value) %>%
    mutate(value = round(value,2))
